{
  \vbox{}
  \vskip0pt plus 1fill
  Für meinen Vater, damit er noch viele schöne \TeX-Graphiken
  erschaffen kann.

  For my father, so that he can still create lots of nice \TeX\ graphics.

  为了我父亲，这样他仍然可以创建很多漂亮的\TeX 图形。

  \vskip1em
  \hfill\emph{Till}
  \vskip0pt plus 3fill

  \parindent=0pt
  Copyright 2007 to 2013 by Till Tantau

  \medskip
  % Permission is granted to copy, distribute and/or modify \emph{the documentation} under the terms of the \textsc{gnu} Free Documentation License, Version 1.2 or any later version published by the Free Software Foundation; with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts. A copy of the license is included in the section entitled \textsc{gnu} Free Documentation License.

  根据\textsc{gnu}自由文档许可证V1.2或自由软件基金会发布的任何更高版本，授予复制，分发和/或修改文档的权限；没有不变的章节，没有前封面文字，也没有后封面文字。 许可证的副本包含在标题为\textsc{gnu}自由文档许可证的章节中。

  \medskip
  % Permission is granted to copy, distribute and/or modify \emph{the code of the package} under the terms of the \textsc{gnu} Public License, Version 2 or any later version published by the Free Software Foundation. A copy of the license is included in the section entitled \textsc{gnu} Public License.

  根据\textsc{gnu}通用公共许可证V2或自由软件基金会发布的任何更高版本的条款，授予复制，分发和/或修改软件包代码的权限。 许可证的副本包含在标题为通用公共许可证的章节中。

  \medskip
  % Permission is also granted to distribute and/or modify \emph{both the documentation and the code} under the conditions of the LaTeX Project Public License, either version 1.3 of this license or (at your option) any later version. A copy of the license is included in the section entitled \LaTeX\ Project Public License.

  在遵循\LaTeX 项目公共许可证（此许可证的V1.3或（由您选择）任何更高版本）的条件下，还授予分发和/或修改文档和代码的权限。 许可证的副本包含在标题为\LaTeX 项目公共许可证的部分中。

  \vbox{}
  \clearpage
}